My title

### 2023-04-01 outputs/paper/paper.qmd
tidying up

Sometime in early October of 2022 there was a chemical shift in my brain and I couldn't stop listening to Taylor Swift. I was a preteen when my best friend's sister showed us Our Song on the family desktop, went on to own a copy of Fearless, and was in the ninth grade when Red came out. My listening tapered off after that, other than ironically dancing to Blank Space in friends kitchens in college, and a road trip a few years ago where we belted Fearless (Three of the four people present were going through something).

All this to say, I can quite confidently say I hadn't listened to much or any Taylor Swift until October, when I couldn't listen to anything other than Fearless or Red when deadlifting, walking to a friend's house, folding laundry, etc. I listened to so much Taylor in that month alone that she ended up as my #4 artist on Spotify Wrapped, which stops collecting its data for the year on October 31st. It didn't even capture what happened to me after Midnights dropped in November.

>>>>

Sometime in early October of 2022 there was a chemical shift in my brain and I couldn't stop listening to Taylor Swift. I couldn't listen to anything other than Fearless or Red when deadlifting, walking to a friend's house, folding laundry, etc. I listened to so much Taylor in that month alone that she ended up as my #4 artist on Spotify Wrapped, which stops collecting its data for the year on October 31st. It didn't even capture what happened to me after Midnights dropped in November.
